\documentclass[margin]{main}
\usepackage[top=0.6in, bottom=0.6in, left=1.1in]{geometry}
\textwidth=5.2in

\begin{document} 
 
\name{\LARGE Chi-Chin Lin \\[12pt]}

\address{
    4F., No.10, Aly. 4, Ln. 201, Yucheng St., \\
    Nangang Dist., Taipei City 115, \\
    Taiwan (R.O.C)
}

\address{
    \hfill +886-923-869-910 \\
    \hfill john.lin.chichin@gmail.com \\
    \hfill \url{http://github.com/averangeall}
}

\begin{resume}
 
\section{EDUCATION}
National Taiwan University, Taipei, Taiwan \hfill Sep. 2012 - Present \\
M.S. in Networking and Multimedia \\
Advisor: Prof. Jane Yung-jen Hsu
 
National Taiwan University, Taipei, Taiwan \hfill Sep. 2008 - Jun.2012 \\
B.S. in Computer Science and Information Engineering \\
Overall GPA: 3.52 / 4, Major GPA: 3.84 / 4


\section{WORK EXPERIENCE}
Software Engineer, Fankudo
\begin{itemize} \itemsep -2pt
    \item[] {\bf Subtitle Editor \& Player} \hfill Sep. 2013 - Present
    \item[] Easy to use web-based subtitle editor and player for translation videos
    \item[] Developed with Javascript, Youtube API and Django
\end{itemize}

{\bf System Administrator}, iAgent Lab \hfill Sep. 2012 - Present
\begin{itemize} \itemsep -2pt
    \item[] Database, web, application, backup and mailing servers
\end{itemize}

Research Assistant, Academia Sinica, with Dr. Wen-Huang Cheng
\begin{itemize} \itemsep -2pt
    \item[] {\bf Object Tracking System} \hfill Mar. 2012 - Jan. 2013
    \item[] Analyse and develop SVM-based video object tracking system
    \item[] Developed with C++, OpenCV
\end{itemize}


\section{RESEARCH PROJECTS}
iAgent Lab, National Taiwan University
\begin{itemize} \itemsep -2pt
    \item[] {\bf 9GAG Lookup} \hfill Sep. 2012 - Present
    \item[] Help new users to fit in websites with dynamically changed topics (e.g. 9GAG)
    \item[] Chrome extension, developed with Javascript and Django
    \item[]
    \item[] {\bf Internet Meme Comprehension} \hfill Oct. 2013 - Present
    \item[] Use crowdsourcing and ConceptNet to find out why a meme joke is funny
    \item[] Combined with 9GAG Lookup
\end{itemize}

Course Projects, National Taiwan University
\begin{itemize} \itemsep -2pt
    \item[] {\bf Can You Do Me a Favor?} \hfill Feb. 2013 - Jul. 2013
    \item[] Select good timing to notify people to solve environmental problems
    \item[] Use regression model to predict interruptibility from users' laptop behaviour
    \item[]
    \item[] {\bf iSee APP} \hfill Sep. 2010 - Jan. 2011
    \item[] Let users to take pictures and record voice on the spot
    \item[] Android APP, with prototype software life cycle model
\end{itemize}


\section{ACADEMIC ACTIVITY}
{\bf Human Resource}, OpenHCI Workshop \hfill Dec. 2011 - Jul. 2012
\begin{itemize} \itemsep -2pt
    \item[] Coordinate between multidisciplinary students (design \& computer science)
\end{itemize}


\section{PROFICIENCY AND INTERESTS}
Computer Languages
\begin{itemize} \itemsep -2pt
    \item[] {\bf Python, C/C++, Javascript}, Java, Perl, PHP, ActionScript
\end{itemize}

Languages
\begin{itemize} \itemsep -2pt
    \item[] Mandarin Chinese (native), English (intermediate)
\end{itemize}

Research Interests
\begin{itemize} \itemsep -2pt
    \item[] {\bf Crowdsourcing, Human-Computer Interaction}, Computational Humor
    \item[] Machine Learning
\end{itemize}

\end{resume}

\end{document}
